---
title: "maya_biosphere_allometric_equations"
output: html_document
date: "2024-11-03"
---

```{r setup, include=FALSE}
library(allometric)
library(tidyverse)
```

```{r}
install_models()
allometric_models <- load_models()
```

```{r}
biomass_models <- allometric_models %>%
  filter(model_type == "tree biomass")
```

Terminalia Amazonia

    Family: Combretaceae
    Genus: Terminalia
    Species: amazonica

Swietenia macrophylla

    Family: Meliaceae
    Genus: Swietenia
    Species: macrophylla

Cedrela odorata

    Family: Meliaceae
    Genus: Cedrela
    Species: odorata

Lysiloma spp.

    Family: Fabaceae (Leguminosae)
    Genus: Lysiloma
    Species: Multiple species within the genus (spp. denotes several species)

Lonchocarpus castilloi

    Family: Fabaceae (Leguminosae)
    Genus: Lonchocarpus
    Species: castilloi

Vochysia hondurensis

    Family: Vochysiaceae
    Genus: Vochysia
    Species: hondurensis

Calophyllum brasiliense

    Family: Calophyllaceae
    Genus: Calophyllum
    Species: brasiliense

```{r}
# Species list
species_list <- list(
  list(family = "Combretaceae", genus = "Terminalia", species = "amazonica"),
  list(family = "Meliaceae", genus = "Swietenia", species = "macrophylla"),
  list(family = "Meliaceae", genus = "Cedrela", species = "odorata"),
  list(family = "Fabaceae", genus = "Lysiloma", species = "spp."),
  list(family = "Fabaceae", genus = "Lonchocarpus", species = "castilloi"),
  list(family = "Vochysiaceae", genus = "Vochysia", species = "hondurensis"),
  list(family = "Calophyllaceae", genus = "Calophyllum", species = "brasiliense")
)
```

No species-specific models are available.
```{r}
# Initialize an empty list to store results
results_list <- list()

# Loop through each species and check for models
for (species_info in species_list) {
  # Create Taxon object
  taxon <- Taxon(
    family = species_info$family,
    genus = species_info$genus,
    species = species_info$species
  )
  
  # Filter for models corresponding to the taxon
  species_models <- allometric_models %>%
    filter(map_lgl(taxa, ~ taxon %in% .))
  
  # Store the results in the results_list
  results_list[[paste(species_info$genus, species_info$species, sep = "_")]] <- species_models
}

results_df <- bind_rows(results_list, .id = "species")
```

```{r}
results_df
```

